---
title: "Shaming"
author: "Var Kurapati"
format: html
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
```
```{r}
#| cache: true
x <- shaming |>
  mutate(civ_engage = primary_00 + general_00 + primary_02 + 
                      general_02 + primary_04 + general_04) |>
  select(primary_06, treatment, sex, age, civ_engage) |>
  drop_na() |>
  mutate(
    voter_class = cut(civ_engage,
                      breaks = c(-Inf, 2, 4, Inf),
                      labels = c("Rarely Vote", "Sometimes Vote", "Always Vote")),
    voter_class = factor(voter_class, 
                         levels = c("Rarely Vote", "Sometimes Vote", "Always Vote")),
    voted = factor(primary_06)
  ) |>
  drop_na()
```

```{r}
x |>
  group_by(treatment, voter_class) |>
  summarize(turnout = mean(primary_06 == "Yes"), .groups = "drop") |>
  ggplot(aes(x = treatment, y = turnout, fill = treatment)) +
  geom_col() +
  geom_text(aes(label = scales::label_percent(accuracy = 0.1)(turnout)),
            vjust = -0.5, size = 3) +
  scale_y_continuous(labels = scales::label_percent()) +
  facet_wrap(~ voter_class) +
  labs(
    title = "August 2006 Primary Turnout by Treatment and Voter Class",
    subtitle = "Neighbors postcard shows largest effect across all voter classes",
    x = "Treatment",
    y = "Turnout Rate",
    fill = "Treatment",
    caption = "Source: Gerber, Green, Larimer 2008 via primer.data::shaming"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_blank())
```

Voter turnout in primary elections is notoriously difficult to influence, yet social-pressure postcards have emerged as one of the most effective get-out-the-vote interventions ever documented. Using data from the Gerber, Green, and Larimer (2008) field experiment on 344,000 registered Michigan voters, we estimate the average causal effect of the Neighbors postcard — which revealed voters' past turnout records to their neighbors — on the probability of voting in the August 2006 primary.






